Curiosity-driven Exploration of Skill Hierarchies

### 2016-01-14 paper1/paper.tex
upd

		Here we want to compare the learning of a structured hierarchy of SAGG-Random modules with the control condition where one sensorimotor model learns
		directly from the whole motor space $M$ to the whole sensori space $S$. 
		For the hierarchical conditions, we randomly choose the module of the hierarchy that will explore at each iteration.
		We also compare Motor Babbling and Goal Babbling in the hierarchical and in the flat hierarchies.
		We use hierarchy H1 (Fig. \ref{H1}), and environmnent E1.
		Exploration: each module will add some exploration noise (Simple TDD).

@@

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-competences.png}}
			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-interests.png}}
			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-events.png}}
			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-obj-explo.png}}
			\caption{Competences, interests, events and object exploration using H0 with Random Goal Babbling}
			\label{resH0GB}
		\end{figure*}

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-competences.png}}
			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-interests.png}}
			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-events.png}}
			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-obj-explo.png}}
			\caption{Competences, interests, events and object exploration using H1 with Random Goal Babbling}
			\label{resH1GB}
		\end{figure*}

		\begin{figure*}[!t]
			\centering
			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp1-event-tool_1.png}}
			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp1-event-obj.png}}
			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp1-event-box_1.png}}\\
			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp1-event-box_2.png}}
			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp1-event-box_3.png}}
			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
			\label{res_xp1_events}
		\end{figure*}

@@

		See Fig. \ref{resH0GB}, \ref{resH1GB}, \ref{res_xp1_events}, \ref{res_xp1_explo}.

@@

		Exploration: each module will add some exploration noise (Simple TDD).

@@

		See Fig. \ref{resI}, \ref{res_xp2_events} and \ref{res_xp2_explo}.

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-competences.png}}
			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-interests.png}}
			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-events.png}}
			\caption{Competences, interests and events using H1 with I}
			\label{resI}
		\end{figure*}

		\begin{figure*}[!t]
			\centering
			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp2-event-tool_1.png}}
			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp2-event-obj.png}}
			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp2-event-box_1.png}}\\
			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp2-event-box_2.png}}
			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp2-event-box_3.png}}
			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
			\label{res_xp2_events}
		\end{figure*}

@@

			\item Condition STDD: (simple TDD): add noise to motor command of each module (pb: interferes with competence estimation?).

			\item Condition EXPLO-N: explore $n$ points and returns the best (exponential if all modules explore $n$ points, so I've implemented that only the chosen module explores $n$ points, and the others add exploration noise)
			%\item Condition BST: balance between self-interest and top-down points (one parameter).

@@

		\begin{figure*}[!t]
			\centering
			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp3-event-tool_1.png}}
			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp3-event-obj.png}}
			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp3-event-box_1.png}}\\
			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp3-event-box_2.png}}
			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp3-event-box_3.png}}
			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
			\label{res_xp3_events}
		\end{figure*}

@@

		\begin{figure*}[!t]
			\centering
			\subfloat[Tool1]{\includegraphics[width=4cm]{./include/xp4-event-tool_1.png}}
			\subfloat[Tool2]{\includegraphics[width=4cm]{./include/xp4-event-tool_2.png}}
			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp4-event-obj.png}}\\
			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp4-event-box_1.png}}
			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp4-event-box_2.png}}
			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp4-event-box_3.png}}
			\caption{Number of touch of tools, object and boxes for each 10000 iterations' bin.}
			\label{res_xp4_events}
		\end{figure*}

>>>>

		Here we want to compare the learning of a structured hierarchy of SAGG-Random modules with the control condition where one sensorimotor model learns
		directly from the whole motor space $M$ to the whole sensori space $S$. 
		For the hierarchical conditions, we randomly choose the module of the hierarchy that will explore at each iteration.
		We also compare Motor Babbling and Goal Babbling in the hierarchical and in the flat hierarchies.
		We use hierarchy H1 (Fig. \ref{H1}), and environmnent E1.
		Exploration: only the chosen module add some exploration noise (No TDD).

@@

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-competences.png}}
			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-interests.png}}
			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-events.png}}
			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-obj-explo.png}}
			\caption{Competences, interests, events and object exploration using H0 with Random Goal Babbling}
			\label{resH0GB}
		\end{figure*}

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-competences.png}}
			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-interests.png}}
			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-events.png}}
			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-obj-explo.png}}
			\caption{Competences, interests, events and object exploration using H1 with Random Goal Babbling}
			\label{resH1GB}
		\end{figure*}

		%\begin{figure*}[!t]
			%\centering
			%\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp1-event-tool_1.png}}
			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp1-event-obj.png}}
			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp1-event-box_1.png}}\\
			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp1-event-box_2.png}}
			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp1-event-box_3.png}}
			%\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
			%\label{res_xp1_events}
		%\end{figure*}

@@

		See Fig. \ref{resH0GB}, \ref{resH1GB}, \ref{res_xp1_explo}.

@@

		Exploration: only the chosen module add some exploration noise (No TDD).

@@

		See Fig. \ref{resI}, \ref{res_xp2_explo}.

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-competences.png}}
			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-interests.png}}
			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-events.png}}
			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-obj-explo.png}}
			\caption{Competences, interests and events using H1 with I}
			\label{resI}
		\end{figure*}

		%\begin{figure*}[!t]
			%\centering
			%\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp2-event-tool_1.png}}
			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp2-event-obj.png}}
			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp2-event-box_1.png}}\\
			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp2-event-box_2.png}}
			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp2-event-box_3.png}}
			%\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
			%\label{res_xp2_events}
		%\end{figure*}

@@

			\item Condition NTDD: (No TDD): Only the babbling module add motor exploration noise.

			\item Condition STDD: (simple TDD): add noise to motor commands of all modules (pb: interferes with competence estimation? loose interest of hierarchy?).

			\item Condition EXPLO-N: the babbling module chooses a goal $s_g$ and infers its motor command $m$. 
					The lower level modules involved will use $m$ as a goal and will try to reach it with $n$ explorative motor commands and will finally return the now infered best motor command.
					Thus there are $n$ explorative actions ($n=3$) for $1$ non explorative action (which still can be surprising and useful in the case of a regressive sensorimotor model).

			\item Condition BST (Balance Self-generation of goals and Top-Down Drive): $0.5$ probability to choose a self-generated goal, and $0.5$ probability to choose a goal around goals asked by upper-level modules.

@@

		%\begin{figure*}[!t]
			%\centering
			%\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp3-event-tool_1.png}}
			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp3-event-obj.png}}
			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp3-event-box_1.png}}\\
			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp3-event-box_2.png}}
			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp3-event-box_3.png}}
			%\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
			%\label{res_xp3_events}
		%\end{figure*}

@@

		%\begin{figure*}[!t]
			%\centering
			%\subfloat[Tool1]{\includegraphics[width=4cm]{./include/xp4-event-tool_1.png}}
			%\subfloat[Tool2]{\includegraphics[width=4cm]{./include/xp4-event-tool_2.png}}
			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp4-event-obj.png}}\\
			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp4-event-box_1.png}}
			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp4-event-box_2.png}}
			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp4-event-box_3.png}}
			%\caption{Number of touch of tools, object and boxes for each 10000 iterations' bin.}
			%\label{res_xp4_events}
		%\end{figure*}
